% Necessity of Identity
\section*{QUESTION 1}
There are contingently true identity statement, but this does not entail the contingency of the notion of identity; on the contrary, identity is necessary. Kripke introduced the notion of rigid designator that designates the same object in all possible worlds in which that object exists. Kripke argues if $a=b$ is true and $a$ and $b$ are rigid designators, then $a=b$ is a necessary truth because the rigid designation implies that $a$ and $b$ both designates the same object in all possible worlds. If $a$ or $b$ are non-rigid designators, then $a=b$ might be a contingently true identity statement. For example, ``Prime Minister of the UK'' is a definite description not applies to a unique object so it is not a rigid designator, then ``Prime Minister of the UK = Rishi Sunak'' is contingently true because the Prime Minister might be succeeded by someone else in the future. This means that such contingency arises from the semantics of the term (the rigidity of designation), rather than from identity. By stipulating that the participating terms are rigid designations, thus removing the semantic layer of contingency, we find that the identity of objects must be necessary.

Kripke's argument for the Necessity of Identity underpins his claim regarding the existence of necessary a posteriori truths. Traditionally, necessary truths were associated with a priori knowledge, and contingent truths with a posteriori knowledge. Kripke challenges this dichotomy by showing how some truths are both necessary and a posteriori. The key to understanding this lies in the nature of rigid designation. For example, we once believed that Hesperus (the evening star) and Phosphorus (the morning star) rigidly designated two different objects, but in fact, they are the same planet. This implies that there are necessary a posteriori truths because, while identity sentences involving two rigid designators are necessary if true, the realisation of their identity is a posteriori, resulting from empirical means and not from logical entailment or semantic analysis alone. In other word, if the morning star is the evening star, then the morning star is necessarily the evening star, but we may not know that the morning star is the evening star, i.e., they designate the same planet, since this is a posteriori knowledge.

\newpage